---
title: "Simulating data and analysing associations between school performance and psychiatric diagnoses"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![DOI](https://zenodo.org/badge/519967868.svg)](https://zenodo.org/badge/latestdoi/519967868)

## Introduction
This document shows how to simulate data, perform the analyses and vizualize the results as described in the article 'School Performance and Later Diagnoses of Non-Affective Psychoses, Bipolar Disorder, and Depression' published in Acta Psychiatrica Scandinavica (DOI:10.1111/acps.13481): <http://doi.org/10.1111/acps.13481>.  

## Load functions

Clone the repository from <https://github.com/davgyl/school_sim.git> and load the functions from the R-scripts.  

## Simulate data

```{r chunk_01}

source("R/dm01_utils.R")
source("R/dm02_pkg.r")
source("R/dm03_sim_data.R")
# Show simulated data
df_tot
```

Descriptive analyses of simulated data

```{r chunk_02}

source("R/mv01_descr_time_event.r")
table_1_data %>% select(-km_fit)
summary_age

```

## Modelling and visualization

To model the associations, run `R/mv03_fit_models.r`. 
To visualize the associations, run `R/mv04_viz.r`. 
To further edit tables and figres, run `R/mv05_tabs_xtra_viz.r`. 

## Versions

R version: `r getRversion()`. Version of packages are shown in the table below. 

```{r chunk_03, echo=FALSE}

tab_pkg_vs <- matrix(NA, nrow = length(packages), ncol = 2)

for(i in 1:length(packages)) {
  tab_pkg_vs[i, 1] <- packages[[i]]
  tab_pkg_vs[i, 2] <- packageVersion(packages[[i]]) %>% paste()
}

kable(tab_pkg_vs, col.names = c("Package", "Version"))

```
